Reasoning about a Capability Machine with Local Capabilities\\ Provably Safe Stack and Return Pointer Management (without OS Support).

### 2017-02-09 csf-2017/paper.tex
Minor changes

\todo[inline]{Add discussion/comparison to other LRs}
% Comparisson of LR to other work:
% - Single othorgonal closure
%   o all capabilities are possible continuations, not just the one we
%   intend to be it.
% - No termination guarantees in observation relation
% - Private/public transitions used like in Dreyer-Neis-Birkedal, but
%   also to  handle the difference in what local and global
%   capabilities can handle.

\subsection{Discussion/comparison with related Dreyer-Neis-Birkedal and with Hur-Dreyer}

\section{Examples}
\begin{figure}[htbp]
  \centering
\begin{lstlisting}
f1: malloc $r_l$ 1
    store $r_l$ 1
    fetch $r_1$ $\adv$
    call $r_1$($[]$,$[r_l]$)
    assert $r_l$ 1
    halt
\end{lstlisting}
  \caption{Simple program that uses a calling convention not relyant
    on the stack}
  \label{fig:prog-f1}
\end{figure}

\begin{figure}[htbp]
  \centering
  \begin{lstlisting}
f2: push 1
    fetch $r_1$ $r_\adv$
    scall $r_1$($[]$,$[]$)
    pop $r_1$
    assert $r_1$ 1
    halt
\end{lstlisting}
  \caption{Simple program that uses a stack-based calling convention.}
  \label{fig:prog-f2}
\end{figure}

>>>>

\subsection{Discussion/comparison with related Dreyer-Neis-Birkedal and with Hur-Dreyer}
\todo[inline]{Add discussion/comparison to other LRs}
% Comparisson of LR to other work:
% - Single othorgonal closure
%   o all capabilities are possible continuations, not just the one we
%   intend to be it.
% - No termination guarantees in observation relation
% - Private/public transitions used like in Dreyer-Neis-Birkedal, but
%   also to  handle the difference in what local and global
%   capabilities can handle.

\section{Examples}

\begin{figure}[htbp]
  \centering
  \begin{lstlisting}
f1: push 1
    fetch $r_1$ $r_\adv$
    scall $r_1$($[]$,$[]$)
    pop $r_1$
    assert $r_1$ 1
    halt
\end{lstlisting}
  \caption{Simple program that uses a stack-based calling convention.}
  \label{fig:prog-f1}
\end{figure}

\begin{figure}[htbp]
  \centering
\begin{lstlisting}
f2: malloc $r_l$ 1
    store $r_l$ 1
    fetch $r_1$ $\adv$
    call $r_1$($[]$,$[r_l]$)
    assert $r_l$ 1
    halt
\end{lstlisting}
  \caption{Simple program that uses a calling convention not relyant
    on the stack}
  \label{fig:prog-f2}
\end{figure}
